Illusion Game Validation (Study 2)

### 2022-09-02 manuscript.Rmd
update

>>>>

We have to keep in mind that individual scores are the result of several layers of simplification: 1) the individual coefficient is that of simpler models that sometimes do not perfectly capture the underlying dynamics (especially in the case of ...), 2) the structural equation model from which they are obtained is also constructed on layers of abstractions. Thus, we wanted to test wether these indices relate to some simple empirical scores, such as the average error rate and RT in the task.

### 2022-09-02 study2/study2.Rmd
update

### Model-based Descriptors

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
data <- rbind(
  extract_random(model_delboeuf_err, "Delboeuf"),
  # extract_random(model_delboeuf_rt, "Delboeuf"),
  extract_random(model_ebbinghaus_err, "Ebbinghaus"),
  # extract_random(model_ebbinghaus_rt, "Ebbinghaus"),
  extract_random(model_rodframe_err, "Rod-Frame"),
  # extract_random(model_rodframe_rt, "Rod-Frame"),
  extract_random(model_verticalhorizontal_err, "Vertical-Horizontal"),
  # extract_random(model_verticalhorizontal_rt, "Vertical-Horizontal"),
  extract_random(model_zollner_err, "Zöllner"),
  # extract_random(model_zollner_rt, "Zöllner"),
  extract_random(model_white_err, "White"),
  # extract_random(model_white_rt, "White"),
  extract_random(model_mullerlyer_err, "Müller-Lyer"),
  # extract_random(model_mullerlyer_rt, "Müller-Lyer"),
  extract_random(model_ponzo_err, "Ponzo"),
  # extract_random(model_ponzo_rt, "Ponzo"),
  extract_random(model_poggendorff_err, "Poggendorff"),
  # extract_random(model_poggendorff_rt, "Poggendorff"),
  extract_random(model_contrast_err, "Contrast")
  # extract_random(model_contrast_rt, "Contrast")
) |> 
  filter(
    !str_detect(Parameter, "Intercept_"),
    !str_detect(Parameter, "Cong"),
    !str_detect(Parameter, "Cong_Prob"),
    !str_detect(Parameter, "Null_"),
    !str_detect(Parameter, "Diff_"))
# unique(data$Parameter)

# data |>
#   # group_by(Illusion_Type, Parameter) |> 
#   # standardize(select="Value") |> 
#   # ungroup() |> 
#   # mutate(order = mean(Value)) |> 
#   # ungroup() |> 
#   # mutate(Participant = fct_reorder(Participant, order)) |> 
#   ggplot(aes(y = Participant, x = Value)) +
#   # ggdist::stat_slabinterval(aes(fill = Illusion_Type, color=Illusion_Type), alpha=0.5) +
#   ggdist::stat_pointinterval(aes(fill = Illusion_Type, color=Illusion_Type), alpha=0.5) +
#   # coord_cartesian(xlim=c(-4, 4)) +
#   facet_wrap(~Parameter, scales = "free_x") +
#   theme(axis.text.y = element_blank())

# df[df$Illusion_Type == "Poggendorff" & df$Participant == "5cbb77bf418c540001641e67_sp53j", ]

random <- data |>
  mutate(Parameter = paste0(Illusion_Type, "_", Parameter),
         Parameter = clean_illusionName(Parameter)) |>
  group_by(Participant, Parameter) |>
  summarize(Score = median(Value, na.rm = TRUE), .groups = "drop") |>
  ungroup() |>
  group_by(Parameter) |>
  mutate(Score = Score / sd(Score, na.rm = TRUE)) |>  # Scale
  ungroup()  |>
  pivot_wider(names_from = Parameter, values_from = Score)

# plot(estimate_density(select(random, -Participant)))
```

@@

## Structure

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
cor <- correlation::correlation(random, redundant = TRUE)

p_data <- cor |>
  mutate(
    Parameter1 = prettify_parameterName(Parameter1),
    Parameter2 = prettify_parameterName(Parameter2)
  ) |>
  correlation::cor_sort(hclust_method = "ward.D2") |>
  cor_lower() |>
  mutate(
    Text = insight::format_value(r, zap_small = TRUE, digits = 3),
    Text = str_replace(str_remove(Text, "^0+"), "^-0+", "-"),
    Parameter2 = fct_rev(Parameter2)
  )

p_data |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  # geom_text(aes(label = Text), size = 2) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  labs(title = "Correlation Matrix", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
```

fa <- parameters::factor_analysis(data,
  cor = as.matrix(cor),
  n = 9,
  rotation = "oblimin",
  fm = "mle",
  sort = TRUE
)

print(tibble::as_tibble(fa), n=30)
plot(fa)
# psych::omega(data, fm = "mle", nfactors=9)
# fa <- psych::fa.multi(as.matrix(cor), nfactors = 3, nfact2 = 1, n.obs = nrow(random))
# psych::fa.multi.diagram(fa)
```

rez <- parameters::n_factors(data, rotation = "oblimin")
plot(rez)

fa2 <- parameters::factor_analysis(data,
  n = 1,
  rotation = "varimax",
  fm = "mle",
  sort = TRUE
)

# psych::schmid(attributes(fa)$model, nfactors = 1)
```

#### Visualization
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
library(ggraph)

@@

### SEM

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
library(lavaan)
library(tidySEM)
library(ggraph)

names <- names(select(random, -Participant))
data <- setNames(as.data.frame(str_split_fixed(names, "_", 3)), c("Illusion_Type", "Parameter", "Model"))
data$Name <- names

m1 <- sem(model = paste0(c(lvl1, lvl2), collapse = "\n"),
          data  = random,
          estimator = "ML",
          missing = "ml",
          bounds = TRUE)  # robust.two.stage

# Model 2 - by Parameter
lvl1 <- paste(data$Parameter, "=~", data$Name)
lvl2 <- paste("I =~", unique(data$Parameter))
resid <- as.data.frame(t(utils::combn(x=unique(data$Parameter), 2)))
resid <- paste(resid$V1, "~~", resid$V2)

m2 <- sem(model = paste0(c(lvl1, lvl2), collapse = "\n"),
          data  = random)

# # Model 3
# lvl1 <- paste(data$Model, "=~", data$Name)
# lvl2 <- paste("G =~", unique(data$Model))
# 
# m2 <- sem(model = paste0(c(lvl1, lvl2), collapse = "\n"),
#            data  = random)

anova(m1, m2)

summary(m1, standardize = TRUE)
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# https://cjvanlissa.github.io/tidySEM/articles/sem_graph.html
edges <- tidySEM::get_edges(m1) |> 
  mutate(color = ifelse(sign(as.numeric(est)) >= 0, "1", "-1"),
         width = abs(as.numeric(est))) |> 
  filter(lhs != rhs)

nodes <- tidySEM::get_nodes(m1) |> 
  mutate(label = prettify_parameterName(name),
         angle = ifelse(grepl("_", name), 90, 0),
         hjust = ifelse(grepl("_", name), 1.01, 0))

tidygraph::tbl_graph(nodes = nodes,
                     edges = edges) |> 
  ggraph(layout = "sugiyama") +
  geom_edge_link(aes(edge_width = width, 
                             color = color,
                             label=est_sig_std), angle_calc="along", label_dodge=unit(-0.015, "npc")) +
  geom_node_point() +
  geom_node_text(aes(label = label, angle = angle, hjust=hjust)) +
  scale_edge_color_manual(values=c("#F44336", "#2196F3"))  +
  scale_y_continuous(expand = expansion(c(.6, .1))) +
  scale_edge_width_continuous(range=c(0.1, 1.5)) +
  guides(edge_colour = "none", edge_width = "none") +
  theme_graph()

r |>
  mutate(label = insight::format_p(p, stars_only=TRUE)) |> 
  ggplot(aes(x = Parameter1, y = Parameter2)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label=label)) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

We have to keep in mind that individual scores are the result of several layers of simplification: 1) the individual coefficient is that of simpler models that sometimes do not perfectly capture the underlying dynamics (especially in the case of ...), 2) the structural equation model from which they are obtained is also constructed on layers of abstractions. Thus, we wanted to test wether these indices relate to some simple empirical scores, such as the average error rate and RT in the task.

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Average for 4 higher level of task difficulty
empirical <- df |>
  filter(Illusion_Effect == "Incongruent") |> 
  group_by(Participant, Illusion_Type, Illusion_Strength) |>
  arrange(Illusion_Difference) |> 
  slice(0:4) |> 
  # select(Illusion_Strength, Illusion_Difference)
  group_by(Participant, Illusion_Type) |>
  summarize(
    TaskHard_Error = sum(Error, na.rm=TRUE) / n(),
    TaskHard_RTMean = mean(ifelse(Error == 0, RT, NA), na.rm=TRUE)
    # Illu_RTSpread = sd(ifelse(Error == 0, RT, NA), na.rm=TRUE),
  ) |>
  ungroup() |> 
  mutate(Illusion_Type = clean_illusionName(Illusion_Type))  |> 
  pivot_wider(names_from = c("Illusion_Type"), values_from = c("TaskHard_Error", "TaskHard_RTMean"), names_glue = "{Illusion_Type}_{.value}")

# Average for 4 higher level of illusion strength
empirical <- df |>
  filter(Illusion_Effect == "Incongruent") |> 
  group_by(Participant, Illusion_Type, Illusion_Difference) |>
  arrange(desc(Illusion_Strength)) |> 
  slice(0:4) |> 
  # select(Illusion_Strength, Illusion_Difference)
  group_by(Participant, Illusion_Type) |>
  summarize(
    IlluStrong_Error = sum(Error, na.rm=TRUE) / n(),
    IlluStrong_RTMean = mean(ifelse(Error == 0, RT, NA), na.rm=TRUE)
    # Diff_RTSpread = sd(ifelse(Error == 0, RT, NA), na.rm=TRUE),
  ) |>
  ungroup() |> 
  mutate(Illusion_Type = clean_illusionName(Illusion_Type))  |> 
  pivot_wider(names_from = c("Illusion_Type"), values_from = c("IlluStrong_Error", "IlluStrong_RTMean"), names_glue = "{Illusion_Type}_{.value}") |> 
  full_join(empirical, by = "Participant") 
```

<!-- ```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE} -->
<!-- rez <- parameters::n_factors(select(empirical, -Participant), n_max=30) -->
<!-- plot(rez) -->

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Correlation
r <- data.frame()
for(ill in c("Delboeuf", 
             "Ebbinghaus",
             "RodFrame",
             "VerticalHorizontal",
             "Zollner",
             "White",
             "MullerLyer",
             "Ponzo",
             "Poggendorff",
             "Contrast"
             )) {
  r <- correlation::correlation(
    data = random |> 
      arrange(Participant) |> 
      data_select(select=ill, regex=TRUE),
    data2 = empirical |>
      data_select(select=ill, regex=TRUE),
    p_adjust="none"
    ) |> 
    mutate(Illusion_Type = ill,
           Parameter1 = prettify_parameterName(Parameter1),
           Parameter2 = prettify_parameterName(Parameter2)) |> 
    select(Illusion_Type, Parameter1, Parameter2, r, p) |> 
    rbind(r)
}

r |>
  mutate(label = insight::format_p(p, stars_only=TRUE)) |> 
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label=label)) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  # facet_wrap(~Illusion_Type, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Save
dfsub |> 
  merge(dfsem, by = "Participant") |> 
  merge(empirical, by = "Participant") |> 
  write.csv("../data/study3.csv", row.names = FALSE)
```

>>>>

### Extraction

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_delboeuf_err.RData")
load("models/model_ebbinghaus_err.RData")
load("models/model_rodframe_err.RData")
load("models/model_verticalhorizontal_err.RData")
load("models/model_zollner_err.RData")
load("models/model_white_err.RData")
load("models/model_mullerlyer_err.RData")
load("models/model_ponzo_err.RData")
load("models/model_poggendorff_err.RData")
load("models/model_contrast_err.RData")

data <- rbind(
  extract_random(model_delboeuf_err, "Delboeuf"),
  # extract_random(model_delboeuf_rt, "Delboeuf"),
  extract_random(model_ebbinghaus_err, "Ebbinghaus"),
  # extract_random(model_ebbinghaus_rt, "Ebbinghaus"),
  extract_random(model_rodframe_err, "Rod-Frame"),
  # extract_random(model_rodframe_rt, "Rod-Frame"),
  extract_random(model_verticalhorizontal_err, "Vertical-Horizontal"),
  # extract_random(model_verticalhorizontal_rt, "Vertical-Horizontal"),
  extract_random(model_zollner_err, "Zöllner"),
  # extract_random(model_zollner_rt, "Zöllner"),
  extract_random(model_white_err, "White"),
  # extract_random(model_white_rt, "White"),
  extract_random(model_mullerlyer_err, "Müller-Lyer"),
  # extract_random(model_mullerlyer_rt, "Müller-Lyer"),
  extract_random(model_ponzo_err, "Ponzo"),
  # extract_random(model_ponzo_rt, "Ponzo"),
  extract_random(model_poggendorff_err, "Poggendorff"),
  # extract_random(model_poggendorff_rt, "Poggendorff"),
  extract_random(model_contrast_err, "Contrast")
  # extract_random(model_contrast_rt, "Contrast")
) |> 
  filter(
    !str_detect(Parameter, "Intercept_"),
    !str_detect(Parameter, "Cong"),
    !str_detect(Parameter, "Cong_Prob"),
    !str_detect(Parameter, "Null_"),
    !str_detect(Parameter, "Diff_"))  |> 
  mutate(Parameter = str_remove(Parameter, "_Prob"))

data |>
  ggplot(aes(y = Median, x = Participant)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Parameter), size=0.5) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_wrap(Parameter~Illusion_Type, scales = "free") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  coord_flip()

random <- data |>
  mutate(Parameter = paste0(Illusion_Type, "_", Parameter),
         Parameter = clean_illusionName(Parameter)) |>
  select(Participant, Parameter, Median) |> 
  pivot_wider(names_from = Parameter, values_from = Median) |> 
  mutate_if(is.numeric, function(x) x / sd(x, na.rm=TRUE))

random[is.na(random)] <- 0
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
cor <- correlation::correlation(random, redundant = TRUE, p_adjust = "none")

p_data <- cor |>
  mutate(
    Parameter1 = prettify_parameterName(Parameter1),
    Parameter2 = prettify_parameterName(Parameter2)
  ) |>
  correlation::cor_sort(hclust_method = "ward.D2") |>
  cor_lower() |>
  mutate(
    Text = insight::format_value(r, zap_small = TRUE, digits = 3),
    Text = str_replace(str_remove(Text, "^0+"), "^-0+", "-"),
    Text = paste0(Text, insight::format_p(p, stars_only = TRUE)),
    Parameter2 = fct_rev(Parameter2)
  )

p_data |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label = Text), size = rel(2), alpha=2/3) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  labs(title = "Correlation Matrix", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# estimate_density(p_data$r, at=as.character(sign(p_data$r))) |> 
#   ggplot(aes(x=x, y=y, color=Group)) +
#   geom_line()
```

fa <- parameters::factor_analysis(data,
  cor = as.matrix(cor),
  n = 7,
  rotation = "oblimin",
  fm = "mle",
  sort = TRUE
)

insight::print_md(fa)

plot(fa) +
  theme_minimal()
# psych::omega(data, fm = "mle", nfactors=7)
# fa <- psych::fa.multi(as.matrix(cor), nfactors = 3, nfact2 = 1, n.obs = nrow(random))
# psych::fa.multi.diagram(fa)
```

rez <- parameters::n_factors(data, rotation = "varimax")
plot(rez)

fa2 <- parameters::factor_analysis(data,
  n = 2,
  rotation = "varimax",
  fm = "mle",
  sort = TRUE
)

insight::print_md(fa2)
```

### Sructural Equation Model

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
library(lavaan)

names <- names(select(random, -Participant))
data <- setNames(as.data.frame(str_split_fixed(names, "_", 2)), c("Illusion_Type", "Parameter"))
data$Name <- names

# Model 0 - EFA
model <- "
I2 =~ RodFrame_Strength + RodFrame_Interaction + VerticalHorizontal_Strength + VerticalHorizontal_Interaction + MullerLyer_Strength + MullerLyer_Interaction + Ponzo_Strength + Ponzo_Interaction
Zollner =~ Zollner_Strength + Zollner_Interaction
White =~ White_Strength + White_Interaction
Ebbinghaus =~ Ebbinghaus_Strength + Ebbinghaus_Interaction
Poggendorff =~ Poggendorff_Strength + Poggendorff_Interaction
Contrast =~ Contrast_Strength + Contrast_Interaction
Delboeuf =~ Delboeuf_Strength + Delboeuf_Interaction
I =~ I2 + Zollner + White + Ebbinghaus + Poggendorff + Contrast
"

m0 <- sem(model = model,
          data  = random,
          bounds = "standard",
          estimator = "ML",
          )

m1 <- sem(model = paste0(c(lvl1, lvl2), collapse = "\n"),
          data  = random,
          bounds = "standard",
          estimator = "ML",
          )

# Model 1b - without Delboeuf
m1b <- sem(model = paste0(c(lvl1, lvl2[lvl2 != "I =~ Delboeuf"]), collapse = "\n"),
          data  = random,
          bounds = "standard",
          estimator = "ML",
          )

# Model 2 - by type
model <- "
Lines =~ MullerLyer_Strength + MullerLyer_Interaction + Ponzo_Strength + Ponzo_Interaction + VerticalHorizontal_Strength + VerticalHorizontal_Interaction
Circles =~ Ebbinghaus_Strength + Ebbinghaus_Interaction + Delboeuf_Strength + Delboeuf_Interaction
Contrast =~ Contrast_Strength + Contrast_Interaction + White_Strength + White_Interaction
Angle =~ Zollner_Strength + Zollner_Interaction + Poggendorff_Strength + Poggendorff_Interaction  + RodFrame_Strength + RodFrame_Interaction
I =~ Lines + Circles + Contrast + Angle 
"

m2 <- sem(model = model,
          data  = random,
          bounds = "standard",
          estimator = "ML"
          )

# Model 3 - by Parameter
lvl1 <- paste(data$Parameter, "=~", data$Name)
lvl2 <- paste("I =~", unique(data$Parameter))
resid <- as.data.frame(t(utils::combn(x=unique(data$Parameter), 2)))
resid <- paste(resid$V1, "~~", resid$V2)

m3 <- sem(model = paste0(c(lvl1, lvl2), collapse = "\n"),
          data  = random,
          bounds = "standard",
          estimator = "ML"
          )

anova(m0, m1, m2)

summary(m1, standardize = TRUE, fit.measures = TRUE)
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# https://cjvanlissa.github.io/tidySEM/articles/sem_graph.html
library(ggraph)
library(tidySEM)

colors <- c("I" = "#9C27B0", 
            "Delboeuf"="#F44336", "Ebbinghaus"="#E91E63",
            "Rod-Frame"="#4CAF50", "Rod\nFrame"="#4CAF50", 
            "Vertical-Horizontal"="#FF9800", "Vertical\nHorizontal"="#FF9800",
            "Zöllner"="#FF5722",
            "White"="#616161", 
             "Müller-Lyer" = "#3F51B5", "Müller\n-Lyer" = "#3F51B5",
            "Ponzo" = "#2196F3",
            "Poggendorff"="#795548",
            "Contrast"="#607D8B", 
            "black"="black")

edges <- tidySEM::get_edges(m1) |> 
  mutate(color = ifelse(sign(as.numeric(est)) >= 0, "1", "-1"),
         width = abs(as.numeric(est)),
         type = ifelse(from == "I", "curved", "straight")) |> 
  filter(lhs != rhs)

nodes <- tidySEM::get_nodes(m1) |> 
  mutate(label = prettify_parameterName(name),
         angle = ifelse(grepl("_", name), 90, 0),
         hjust = case_when(
           grepl("_", name) ~ 1.15,
           name == "I" ~ 0.5,
           TRUE ~ 0.5),
         size = case_when(
           grepl("_", name) ~ 1,
           name == "I" ~ 7,
           TRUE ~ 6),
         textsize = case_when(
           grepl("_", name) ~ 1,
           name == "I" ~ 3,
           TRUE ~ 1.1),
         face = case_when(
           grepl("_", name) ~ "italic",
           name == "I" ~ "bold",
           TRUE ~ "plain"),
         color = str_remove_all(label, " - .*"),
         textcolor = ifelse(grepl("_", name), "black", "white"),
         label = str_remove_all(label, ".* - "),
         label = str_replace(label, "Müller-Lyer", "Müller\n-Lyer"),
         label = str_replace(label, "Rod-Frame", "Rod\nFrame"),
         label = str_replace(label, "Vertical-Horizontal", "Vertical\nHorizontal"),
         family = ifelse(name == "I", "serif", "sans"))

p <- tidygraph::tbl_graph(nodes = nodes, edges = edges) |> 
  ggraph(layout = "sugiyama") +
  geom_edge_arc(aes(filter=type!="straight",
                    edge_width = width,
                    color = color,
                    label=est_std),
                strength = 0.03 * c(-1, -1, 1, 1, 1, 1, -1, -1, -1, -1),
                angle_calc="along",
                label_dodge=unit(-0.015, "npc")) +
  geom_edge_link(aes(filter=type=="straight",
                     edge_width = width, 
                     color = color,
                     label=est_std), 
                 angle_calc="along", 
                 label_dodge=unit(-0.015, "npc")) +
  geom_node_point(aes(shape = shape, color=color, size=size)) +
  geom_node_text(aes(label = label, angle = angle, hjust=hjust),
                 color=nodes$textcolor, 
                 fontface=nodes$face,
                 size = rel(nodes$textsize*3),
                 family=nodes$family) +
  scale_y_continuous(expand = expansion(c(.6, .1))) +
  scale_edge_width_continuous(range=c(0.1, 1.5)) +
  scale_edge_color_manual(values=c("1"="#263238", "-1"="#B71C1C")) +
  scale_color_manual(values=colors, guide="none") +
  scale_shape_manual(values=c("oval"="circle", "rect"="square"), guide="none") +
  scale_size_continuous(range = c(2, 27), guide="none") +
  guides(edge_colour = "none", edge_width = "none") + 
  labs(title = "Structural Equation Model")  +
  theme_graph() +
  theme(plot.title = element_text(hjust=0.5))
p
save(p, file="models/sem.Rdata")

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Average for 4 higher level of task difficulty
empirical <- df |>
  filter(Illusion_Effect == "Incongruent") |> 
  group_by(Participant, Illusion_Type, Illusion_Strength) |>
  arrange(Illusion_Difference) |> 
  slice(0:2) |> 
  # select(Illusion_Strength, Illusion_Difference)
  group_by(Participant, Illusion_Type) |>
  summarize(
    TaskHard_Error = sum(Error, na.rm=TRUE) / n(),
    TaskHard_RTMean = mean(ifelse(Error == 0, RT, NA), na.rm=TRUE)
    # Illu_RTSpread = sd(ifelse(Error == 0, RT, NA), na.rm=TRUE),
  ) |>
  ungroup() |> 
  mutate(Illusion_Type = clean_illusionName(Illusion_Type))  |> 
  pivot_wider(names_from = c("Illusion_Type"), values_from = c("TaskHard_Error", "TaskHard_RTMean"), names_glue = "{Illusion_Type}_{.value}")

# Average for 4 higher level of illusion strength
empirical <- df |>
  filter(Illusion_Effect == "Incongruent") |> 
  group_by(Participant, Illusion_Type, Illusion_Difference) |>
  arrange(desc(Illusion_Strength)) |> 
  slice(0:2) |> 
  # select(Illusion_Strength, Illusion_Difference)
  group_by(Participant, Illusion_Type) |>
  summarize(
    IlluStrong_Error = sum(Error, na.rm=TRUE) / n(),
    IlluStrong_RTMean = mean(ifelse(Error == 0, RT, NA), na.rm=TRUE)
    # Diff_RTSpread = sd(ifelse(Error == 0, RT, NA), na.rm=TRUE),
  ) |>
  ungroup() |> 
  mutate(Illusion_Type = clean_illusionName(Illusion_Type))  |> 
  pivot_wider(names_from = c("Illusion_Type"), values_from = c("IlluStrong_Error", "IlluStrong_RTMean"), names_glue = "{Illusion_Type}_{.value}") |> 
  full_join(empirical, by = "Participant") 
```

r |>
  mutate(label = insight::format_p(p, stars_only=TRUE),
         Type = ifelse(str_detect(Parameter2, "_Error"), "Error", "RT")) |> 
  ggplot(aes(x = Parameter1, y = Parameter2)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label=label)) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  facet_wrap(~Type, scales="free") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust=1)) 
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Correlation
r <- data.frame()
for(ill in c("Delboeuf", 
             "Ebbinghaus",
             "RodFrame",
             "VerticalHorizontal",
             "Zollner",
             "White",
             "MullerLyer",
             "Ponzo",
             "Poggendorff",
             "Contrast"
             )) {
  r <- correlation::correlation(
    data = dfsem |> 
      arrange(Participant),
    data2 = empirical |>
      data_select(select=ill, regex=TRUE),
    p_adjust="none"
    ) |> 
    mutate(Illusion_Type = ill,
           Parameter1 = prettify_parameterName(Parameter1),
           Parameter2 = prettify_parameterName(Parameter2)) |> 
    select(Illusion_Type, Parameter1, Parameter2, r, p) |> 
    rbind(r)
}

r |>
  mutate(label = insight::format_p(p, stars_only=TRUE)) |> 
  ggplot(aes(x = Parameter1, y = Parameter2)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label=label)) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  # facet_wrap(~Illusion_Type, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

### GARBAGE
<!-- ```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE} -->
<!-- rez <- parameters::n_factors(select(empirical, -Participant), n_max=30) -->
<!-- plot(rez) -->

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
library(ggraph)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Save
dfsub |> 
  merge(dfsem, by = "Participant") |> 
  write.csv("../data/study3.csv", row.names = FALSE)
```
